\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-06-30 paper/paper.tex
compile-o-mat

\subsubsection{Estimating the bias}
For most of the observed range (1941 to 2010) we do not have any information how many tax units fall into the category of having income that is not zero but is too little to qualify for federal taxation (lets call those ``zeros'' for convenience) . However starting 1995, the FTA provides exactly this information for each canton. This enables us to estimate the bias we introduce for each canton and each period between 1995 and 2010. Consequently we can obtain information whether the bias is stable over time (which makes it possible to safely interpret the changes of inequality over time) and whether the bias is different for each canton. \textcolor{red}{Unterschiede zwischen Kantonen wären gut um zu argumentieren, dass andere Länder auch davon betroffen sind, in etwa sowas wie ``je höher der Steuerfreibetrag, umso stärker der Bias''. Länder de erst sehr spät besteuern (und über nicht Besteuerte dann auch nicht Buch führen) haben einen krassen Bias. Wir könnten dann empfehlungen geben, ab welchem Perzentil man save interpretieren kann oder so.}

One can take a first look at the descriptives plotting the share of zeros over time seperately for each canton.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/zero_descriptives1}

\includegraphics[width=\maxwidth]{figure/zero_descriptives2}

@@

We can see multiple things here:

\begin{enumerate}
\item There is a small overall upward trend which we assume to be the Federal Administrations inflation adjustments to the tax threshold.
\item Geneva and Tessin show wild changes but those might be explained by the tax gap ("Bemessungslücke") that people exploited when the cantons changed the tax system. It remains unclear however why we can't see similar patter within other cantons.
\item There is some variance and we see different patterns over time and cantons. When estimating Gini coefficients or the like we must therefore assume that ignoring ``the zeros'' leads to a bias that is not stable over time.
\end{enumerate}

We might try two strategies to moderate the problem:

\begin{enumerate}
\item Add the zeros as a separate group
\item Fit a model to predict the inequality measure (e.g. the Gini coefficient) using the share of zeros as a predictor
\end{enumerate}

By adding the zeros as a separate group we face several problems. With the exception of Geneva 1995/96 Pareto interpolation of percentiles p20 and above seems viable. Low percentiles however would need to be extrapolated so we might impose unrealistic assumptions. Even when estimating ``safe'' measures above p20 (better p50) or a Gini coefficient we need to make an assumption about the income structure of that group (a distribution, a mean income or zero-income). To be consistent with the measure of ``taxable income'' we could assume an income of zero for that group, calculate Gini coefficients and compare them with the original (uncorrected/plain) version. To get a rough number we could (by cantons) check the squared correlation between plain and corrected Gini.

The second approach however is more robust as we do not impose additional assumptions but instead exercise some curve fitting.

@@

The model outputs a test statisic for each canton that tells us whether the variation of the zero-rate over time leads to a significant deviation from the typical ``canton gini-level''. As the model has a decent fit we are not in great danger of omitted variable bias. Using a joint F-Test we can now test if all canton interactions are zero.

In our case we can clearly reject the hypothesis that all interactions are zero ($p=0$). This leads to the conclusion  that Gini coefficients are biased by the variation of the zero-share which is kind of obvious but at the same time we can use the model to report adjusted Gini coefficients. For example one might be interested in how inequality would had developed if the zero-share would have been constant over time. (Note RF: predict all data point using canton, time and the initial OR final zero-share to homogenize the time series)
Furthermore we can quantify how large the bias is and we can do this separately for tax periods or separately for cantons.

For all cantons:

We can see the the model fit reduces to explaining 61.5\% of the Gini variation versus 92.6\% when the information from the zero-shares was used. Although this so some extent attributable to the additional 26 parameters: this is huge.

The model indicates some cases that deserve more attention: Schwyz (positive coefficient) and Geneva (negative coefficient) and the tax period 2000 as well as the most recent periods.

A positive coefficient (e.g. Schwyz) can be read as follows: In periods with many zeros we measure higher Gini coefficients. We can derive, that the distribution of income is more skewed for high incomes than for low incomes. Simply speaking, the contrast between low and middle class is less pronounced than the contrast between middle and top class. One possible explanation would be that incomes stem from two different populations: 1) the people of Schwyz who possibly follow a log-normal or gamma distribution and 2) particularly rich people who moved to Schwyz to avoid taxes.

@@

\subsection{Statistical units}

% Achtung: Das kann doch nicht stimmen, dass wir hier eine Reihe ab 1993 vorliegen haben.
% Die ESTV-Zahlen beginnen ab 1995/1996... Ist das jetzt eine Periode, wo man noch Gesamtschweizerische Reihen rekonstruieren kann?

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/With_and_without_equivalence_scale}

@@

% Es stellt sich die Frage für welchen Zeitraum der Vergleich gemacht wird.
% Ich schlage vor, der Vergleich wird mit den Brülhartdaten gemacht und der Vergleich soll von 2003 bis 2010 reichen

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/Comparing_2003_to_20101} 
\begin{kframe}\begin{verbatim}
## Smoothing using 0.4
## Smoothing using 0.4
## Smoothing using 0.4
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/Comparing_2003_to_20102}

@@

% Report Polarization index

\emph{Gini coefficients considering mean-tested benefits}

% Wollen wir das ?berhaupt machen?

% Zero-shares (alter Textbaustein)
%Estimation using population statistics (1945/46-1993/94) and official tax administration statistics (1995/96 and later) 
% Das allenfalls in der Methodensection machen?
% Vergleich mit der Dell-Reihe zu Non-fillers
% Überschneidungen gib es leider nicht 
% Interessant wäre es auch, zu sehen ob es Brüche in den Zeitreihen der Zahl der Steuerpflichtigen und jener ohne Besteuerung gibt.

@@

%ABBILDUNGEN ZUM VERGLEICH NORMAL-/SONDERFÄLLE
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/specialcases93941}

\includegraphics[width=\maxwidth]{figure/specialcases93942}

\includegraphics[width=\maxwidth]{figure/specialcases93943} 
\begin{kframe}\begin{verbatim}
## Smoothing using 0.4
## Smoothing using 0.4
## Smoothing using 0.4
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/specialcases93944}

@@

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/specialcases101}

\includegraphics[width=\maxwidth]{figure/specialcases102}

\includegraphics[width=\maxwidth]{figure/specialcases103} 
\begin{kframe}\begin{verbatim}
## Smoothing using 0.4
## Smoothing using 0.4
## Smoothing using 0.4
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/specialcases104}

@@

@@

\emph{Income measures with and without zeros}

taxable income with and without zeros

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/with_without_zeros1}

\includegraphics[width=\maxwidth]{figure/with_without_zeros2}

@@

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/setup_data1} 
\begin{kframe}\begin{verbatim}
## Smoothing using 0.4
## Smoothing using 0.4
## Smoothing using 0.4
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/setup_data2}

\includegraphics[width=\maxwidth]{figure/setup_data3} 
\begin{kframe}\begin{verbatim}
## Smoothing using 0.4
## Smoothing using 0.4
## Smoothing using 0.4
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/setup_data4}

\includegraphics[width=\maxwidth]{figure/setup_data5} 
\begin{kframe}\begin{verbatim}
## Smoothing using 0.4
## Smoothing using 0.4
## Smoothing using 0.4
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/setup_data6}

@@

@@

%Methodological Main findings 
%(1) Tax data is useful because its possible to construct consistent measures over time for income and wealth, which is useful to asses changes over time and conducted studies about impact of structural changes.(2) Concerning accuracy of inequality tax data has advantages and shortcomings. Its superior to survey data, because the latter is affected by non-responded bias. Tax data includes data about the whole population  [was finden wir wegen den Nullern raus] . or at least it should (tax evasion).(3) The FTA-Tax data has different shortcomings, which cannot be handled like a measure of income and wealth which (a) cannot be corrected for household size and (b) is neither a pre-transfer nor a post-transfer income measure. Therefor its comparability with other surveys is harsh as long as the main sources of data on inequality are based on measures, which cannot be replicated with taxable income. This FTA-Tax data problem can be handled with non-aggregated tax-data .

@@

% M

>>>>

\subsubsection{Non-taxed}
Some tax units are missing in the FTA data as they do not qualify for taxation below a certain income threshold. The income distribution is therefore cut at the left end. For most of the observed range it is not documented how many tax units fall into this unobserved category. Since 1995 however the FTA provides the number of people not being taxed (we will call these tax units ``zeros''). From 1995 to 2010 we can therefore estimate the bias we introduce when ignoring the zeros. In this section we will try to analyze whether the bias is stable over time (and cantons). If the bias was stable over time, we could still analyze trends and changes of inequality no matter how severe the bias is.

First it is useful to look at the descriptives plotting the share of zeros over time.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/zero_descriptives}

@@

The number of zeros increased slightly. Different interpretations seems possible. The increased share of zeros could be driven by the FTA's inflation adjustments or an increase in social deductions. Another plausible explanation is the increasing number of unmarried couples filling in two separate tax forms instead of one so we observe two ``small'' incomes instead of one ``large'' income, thus inflating the number of people falling below the taxation threshold.

%\begin{enumerate}
%\item There is a small overall upward trend which we assume to be the Federal Administrations inflation adjustments to the tax threshold.
%\item Geneva and Tessin show wild changes but those might be explained by the tax gap ("Bemessungslücke") that people exploited when the cantons changed the tax system. It %remains unclear however why we can't see similar patter within other cantons.
%\item There is some variance and we see different patterns over time and cantons. When estimating Gini coefficients or the like we must therefore assume that ignoring ``the zeros'' leads to a bias that is not stable over time.
%\end{enumerate}

As we want to report reliably inequality time series we pursue two strategies:

\begin{enumerate}
\item Add the zeros as a separate group
\item Carry out a statistical test whether the share of zeros alters the Gini coefficient
\end{enumerate}

By adding the zeros back as a separate group we need to make an assumption about the income distribution within that group. We know these cases had incomes between zero and the threshold (usually around 15.000 CHF for the period 1995-2010). In figure WITHWITHOUTZEROSTIMESERIES we show Gini coefficients calculated under the assumption of the zeros being zero. This is problematic for two reasons: first we know these units might earn more (up to the threshold) so Ginis calculated on this assumptions will be too high. Second we assume the zero group to be perfectly homogenous which on the contrary has a lowering effect on the Gini coefficient. Therefore we must at least assume a distribution for the zeros that has some variance and ranges from zero to the threshold. We decided to use the most simple approach fulfilling both criteria which is to interpolate a uniform distribution between zero and each tax periods threshold.

The second approach investigates whether the FTA time series is suitable to analyze trends of inequality even if the inequality measures are biased. We can do this by regressing the inequality measure (here the Gini coefficient) on the share of zeros. Simply spoken we test if cutting a larger (left) tail of the distribution changes the shape of the distribution. We include Gini coefficient for all cantons in our analyses to improve the power of our statistical test\footnote{Furthermore without cantonal data (but only data for aggregate Switzerland) it is impossible to distinguish whether inequality changed due to the number of unobserved people or any other variable that changed over time)}.

@@

The model outputs a test statistic for each canton that tells us whether the variation of the zero-rate over time leads to a significant deviation from the typical ``canton gini-level''. As the model has a decent fit we are not in great danger of omitted variable bias. Using a joint F-Test we can now test if all canton interactions are zero.

In our case we can clearly reject the hypothesis that all interactions are zero ($p=0$). This leads to the conclusion that Gini coefficients are biased by the variation of the zero-share. As a minimum a researcher using tax data should therefore control the share of unobserved people, while the best solution is to thoroughly the mechanisms behind a change in the zero share (e.g. this might be due to increased unemployment in one period and due to changes of the tax system in another period.). Fortunately the model coefficient of Switzerland as a whole is not significant suggesting that the cantonal biases cancel each other out. This seems plausible if the phenomenon is e.g. driven by tax competition because most of the ``tax optimization'' happens within Switzerland.
% which is kind of obvious but at the same time we can use the model to report adjusted Gini coefficients. For example one might be interested in how inequality would had developed if the zero-share would have been constant over time. (Note RF: predict all data point using canton, time and the initial OR final zero-share to homogenize the time series)
%Furthermore we can quantify how large the bias is and we can do this separately for tax periods or separately for cantons.

%For all cantons:

%<<magnitude_of_bias>>=
%reduced_fit <- lm(G_steink~kanton+factor(steuerperiode),data=df)
%#summary(reduced_fit)
%@

%We can see the the model fit reduces to explaining 61.5\% of the Gini variation versus 92.6\% when the information from the zero-shares was used. Although this so some extent attributable to the additional 26 parameters: this is huge.

%The model indicates some cases that deserve more attention: Schwyz (positive coefficient) and Geneva (negative coefficient) and the tax period 2000 as well as the most recent periods.

Figure COEFPLOT can be read as follows: A positive coefficient (e.g. Schwyz) states that we measure higher Gini coefficients in periods with many zeros. We can derive, that the distribution of incomes is more skewed for high incomes than for low incomes. Simply speaking, the contrast between low and middle class is less pronounced than the contrast between middle and top class. One possible explanation would be that incomes stem from two different distributions (populations): 1) local people of Schwyz who follow a less skewed distribution and 2) particularly rich people who moved to Schwyz (to avoid taxes).

@@

\emph{Equivalence scale}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/equivalencescale}

@@

% Vergleich über die Zeit da, wo zum ersten Mal Gesamtschweizerische Daten vorliegen bis zur neusten Reihe: 2003 vs 2010

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## Smoothing using 0.4
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/reldist20032010}

@@

\begin{kframe}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Loading required package: splines}}\end{kframe}% latex.default(format(c(`Median Index` = med, `Lower Index` = lower,      `Upper Index` = upper, `$\\Delta$ Gini` = dgini), digits = ndig),      file = "", title = title) 
%
\begin{table}[!tbp]
\begin{center}
\begin{tabular}{ll}
\hline\hline
\multicolumn{1}{l}{Inequality Indices}&\multicolumn{1}{c}{}\tabularnewline
\hline
Median Index&0.058\tabularnewline
Lower Index&0.072\tabularnewline
Upper Index&0.045\tabularnewline
$\Delta$ Gini&0.025\tabularnewline
\hline
\end{tabular}
\end{center}
\end{table}

% Der Vergleich liesse sich auch mit den Perzentilen des Reineinkommens auf der Grundlage der aggregierten ESTV-Daten machen. Dies wäre ein Vorteil, falls die Nuller in den Individual-Daten der ESTV als Nuller geführt sind und nicht mit dem tatsächlichen steuerbaren Einkommen

% FEHLT: Tabelle mit Median, lower und upper polaritätsindex plus Gini bzw. Differenz der Ginis

@@

% Variante 1993/1994

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## Smoothing using 0.4
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/specialcases9394}

@@

% latex.default(format(c(`Median Index` = med, `Lower Index` = lower,      `Upper Index` = upper, `$\\Delta$ Gini` = dgini), digits = ndig),      file = "", title = title) 
%
\begin{table}[!tbp]
\begin{center}
\begin{tabular}{ll}
\hline\hline
\multicolumn{1}{l}{Inequality Indices}&\multicolumn{1}{c}{}\tabularnewline
\hline
Median Index&0.020\tabularnewline
Lower Index&0.029\tabularnewline
Upper Index&0.010\tabularnewline
$\Delta$ Gini&0.013\tabularnewline
\hline
\end{tabular}
\end{center}
\end{table}

@@

% Variante 2010

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## Smoothing using 0.4
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/specialcases10}

@@

% latex.default(format(c(`Median Index` = med, `Lower Index` = lower,      `Upper Index` = upper, `$\\Delta$ Gini` = dgini), digits = ndig),      file = "", title = title) 
%
\begin{table}[!tbp]
\begin{center}
\begin{tabular}{ll}
\hline\hline
\multicolumn{1}{l}{Inequality Indices}&\multicolumn{1}{c}{}\tabularnewline
\hline
Median Index&0.170\tabularnewline
Lower Index&0.206\tabularnewline
Upper Index&0.134\tabularnewline
$\Delta$ Gini&0.044\tabularnewline
\hline
\end{tabular}
\end{center}
\end{table}

@@

\emph{taxable income with and without non-taxed}

% Beim Vergleich der Datensätze unterschieden nach nur besteuerten und unter berücksichtigung der nicht besteuerten, stellt sich die Frage wie die unteren Einkommen imputiert werden. Wir haben uns überlegt, dass dies vor allem singles (übrige) betrifft, weil Familien in den unteren Einkommenstabellen bereits sehr selten vorkommen. Deswegen reicht es nur die Untergrenze für singels zu berücksichtigen. Diese liegt 2010 bei 16'900 verändert sich aber über die Zeit

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/with_without_zeros_Gini}

@@

% Wenn wir annehmen, dass die Brülhart-Daten, sowohl die unteren als auch die oberen Perzentile angemessen abbildend, dann reicht der Vergleich. Etwas merkwürdig ist es jetzt, wenn wir die Gini-Reihe mit den ESTV Daten machen und dann den Vergleich mit den Brülhartdaten

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/with_without_zeros_RelDist_mitBruelhart1} 
\begin{kframe}\begin{verbatim}
## Smoothing using 0.4
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/with_without_zeros_RelDist_mitBruelhart2}

% latex.default(format(c(`Median Index` = med, `Lower Index` = lower,      `Upper Index` = upper, `$\\Delta$ Gini` = dgini), digits = ndig),      file = "", title = title) 
%
\begin{table}[!tbp]
\begin{center}
\begin{tabular}{ll}
\hline\hline
\multicolumn{1}{l}{Inequality Indices}&\multicolumn{1}{c}{}\tabularnewline
\hline
Median Index&-0.1084\tabularnewline
Lower Index&-0.2155\tabularnewline
Upper Index&-0.0013\tabularnewline
$\Delta$ Gini&-0.0952\tabularnewline
\hline
\end{tabular}
\end{center}
\end{table}

% Wenn etwas bei den unteren Perzentilen nicht stimmt (nicht Besteuerte als Null gewertet), dann müsste der Vergleich mit den ESTV-Nullern gemacht werden.
% Es ist mir aktuell unklar bei welchem Datensazt jetzt die Perzentile mit imputierten Nullern vorliegt.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: Objekt 'estvReink' nicht gefunden}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: undefined columns selected}}\end{kframe}
\includegraphics[width=\maxwidth]{figure/with_without_zeros_RelDist_mitESTV1} 
\begin{kframe}\begin{verbatim}
## Smoothing using 0.4
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/with_without_zeros_RelDist_mitESTV2}

% latex.default(format(c(`Median Index` = med, `Lower Index` = lower,      `Upper Index` = upper, `$\\Delta$ Gini` = dgini), digits = ndig),      file = "", title = title) 
%
\begin{table}[!tbp]
\begin{center}
\begin{tabular}{ll}
\hline\hline
\multicolumn{1}{l}{Inequality Indices}&\multicolumn{1}{c}{}\tabularnewline
\hline
Median Index&-0.1084\tabularnewline
Lower Index&-0.2155\tabularnewline
Upper Index&-0.0013\tabularnewline
$\Delta$ Gini&-0.0952\tabularnewline
\hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## Smoothing using 0.4
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/BruelhartvsHABE1} 
\begin{kframe}\begin{verbatim}
## Smoothing using 0.4
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/BruelhartvsHABE2}

\includegraphics[width=\maxwidth]{figure/BruelhartvsHABE3} 
\begin{kframe}\begin{verbatim}
## Smoothing using 0.4
## Smoothing using 0.4
## Smoothing using 0.4
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/BruelhartvsHABE4}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/benplot}

@@

%Methodological Main findings 
%(1) Tax data is useful because it's possible to construct consistent measures over time for income and wealth, which is useful to asses changes over time and conducted studies about impact of structural changes.(2) Concerning accuracy of inequality tax data has advantages and shortcomings. It's superior to survey data, because the latter is affected by non-responded bias. Tax data includes data about the whole population [was finden wir wegen den Nullern raus] . or at least it should (tax evasion).(3) The FTA-Tax data has different shortcomings, which cannot be handled like a measure of income and wealth which (a) cannot be corrected for household size and (b) is neither a pre-transfer nor a post-transfer income measure. Therefor it's comparability with other surveys is harsh as long as the main sources of data on inequality are based on measures, which cannot be replicated with taxable income. This FTA-Tax data problem can be handled with non-aggregated tax-data .

@@

% Mögliche Einstiegsfloskel
% This article highlights the main disparities between taxdata based assessment of inequality opossed to given standard concepts of inequality as it is mainly applied with household-surveys. We reflected all important concerns based on the case of Switzerland.
